### 2023-02-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@1c122f954c03d81853ba457abc14ae434005d61d 🚀

>>>>

\hypertarget{acknowledgement}{%
\section{Acknowledgement}\label{acknowledgement}}

We acknowledge that this study was conducted on land within the
traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. This
work was supported by the Institute for Data Valorisation (IVADO) and
the Natural Sciences and Engineering Research Council of Canada (NSERC)
Collaborative Research and Training Experience (CREATE) program, through
the Computational Biodiversity Science and Services (BIOS²) program. A
special thank to all members of the Black Holes and Revelations working
group (organized by BIOS²) for their insightful discussions and valuable
feedbacks on this manuscript.
